### 2025-03-06 tutorials/getstarted.qmd
Update tutorials/getstarted.qmd
Co-authored-by: Mateusz Baran <mateuszbaran89@gmail.com>

We obtain the [special Euclidean group](../groups/special_euclidean_group.md)
$\mathrm{SE}(3) = \mathrm{SO}(3) ⋉ T(3)`` where the group action is the one discussed as an example before.

>>>>

We obtain the [special Euclidean group](../groups/special_euclidean_group.md)
$\mathrm{SE}(3) = \mathrm{SO}(3) ⋉ T(3)$ where the group action is the one discussed as an example before.
